---
name: Amelia A.
surname: Miramonti
position: "Postdoctoral Researcher and Adjunct Faculty"
address: "Nebraska Evaluation and Research Center · University of Nebraska–Lincoln"
email: "amiramonti@nebraska.edu"
github: "amelia-m"
linkedin: "amelia-miramonti"
orcid: "0000-0002-0277-4064"
scholar: "AcbJlasAAAAJ"
researchgate: "Amelia-Miramonti"
www: "osf.io/zk8rv/"
headcolor: "009ACD"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::latexcv:
    theme: classic
engine: knitr
params:
  # ── Section toggles (all TRUE = full academic CV) ──
  show_manuscripts:     true    # Manuscripts in Progress (under Refereed Articles)
  show_preprints:       true    # Preprints (under Refereed Articles)
  show_presentations:   true    # Papers Presented at Professional Meetings
  show_mentoring:       true    # Mentoring Experience
  show_training:        true    # Additional Professional Training
  show_credentials:     true    # Professional Credentials
  show_lab_skills:      true    # Technical Skills — Laboratory Assessments
  show_languages:       true    # Technical Skills — Languages
  show_profiles:        true    # Online Profiles
  show_coursework:      false   # Graduate Coursework (supplement; off by default)
  coursework_detail:    "full"  # "summary", "full", or "both"
header-includes:
  # Clear fancyhdr defaults — the latexcv template sets \pagestyle{fancy}
  # without explicit \lhead/\chead/\rhead, so fancyhdr falls back to printing
  # \rightmark (the current section/subsection title) as a running header on
  # every page after the first. That surfaces as orphaned, clipped-looking
  # text near the top margin (see bib_review_notes / layout fix 2026-04-11).
  - \fancyhf{}
  - \renewcommand{\headrulewidth}{0pt}
  # Prevent widowed section/subsection headings at page bottom.
  # \needspace reserves minimum vertical space; if insufficient, forces a
  # page break *before* the heading instead of after it.
  - \usepackage{needspace}
  - \let\oldsection\section
  - \renewcommand{\section}[1]{\needspace{8\baselineskip}\oldsection{#1}}
  - \let\oldsubsection\subsection
  - \renewcommand{\subsection}[1]{\needspace{6\baselineskip}\oldsubsection{#1}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(vitae)
library(tibble)
library(dplyr)
library(purrr)
library(glue)
library(conflicted)
library(scholar)

conflicts_prefer(dplyr::filter, dplyr::select, .quiet = TRUE)

source("cv_data.R")

if (params$show_coursework) {
  source("coursework_data.R")
}

# Fetch live citation metrics from Google Scholar.
# Falls back to last-known values if Scholar is unreachable at render time.
.scholar_id <- "AcbJlasAAAAJ"
.metrics <- tryCatch(
  scholar::get_profile(.scholar_id),
  error = function(e) NULL
)
if (!is.null(.metrics)) {
  .cites   <- format(.metrics$total_cites, big.mark = ",")
  .hindex  <- .metrics$h_index
  .i10     <- .metrics$i10_index
  .metrics_date <- format(Sys.Date(), "%Y-%m-%d")
} else {
  .cites        <- "1,727"   # last known
  .hindex       <- 18
  .i10          <- 20
  .metrics_date <- "2026-04-11"
}
```

# Education

```{r education}
education_data |>
  detailed_entries(
    what  = degree,
    when  = dates,
    with  = institution,
    where = location,
    why   = details
  )
```

`r if (params$show_coursework) "# Graduate Coursework"`

```{r coursework-summary, eval=params$show_coursework && params$coursework_detail %in% c("summary", "both")}
coursework_data |>
  filter(type == "course") |>
  count(area, sort = TRUE) |>
  brief_entries(
    what = area,
    with = glue("{n} courses")
  )
```

```{r coursework-full, eval=params$show_coursework && params$coursework_detail %in% c("full", "both")}
coursework_data |>
  filter(type %in% c("course", "practicum")) |>
  mutate(
    # sort semesters chronologically
    .sort_key = case_when(
      grepl("Spring", semester) ~ paste0(sub("Spring ", "", semester), "-1"),
      grepl("Summer", semester) ~ paste0(sub("Summer ", "", semester), "-2"),
      grepl("Fall",   semester) ~ paste0(sub("Fall ", "",   semester), "-3"),
      TRUE ~ semester
    )
  ) |>
  arrange(institution, .sort_key) |>
  detailed_entries(
    what  = title,
    when  = semester,
    with  = code,
    where = institution
  )
```

# Academic Professional Experience

```{r positions}
positions_data |>
  detailed_entries(
    what  = title,
    when  = dates,
    with  = unit,
    where = institution,
    why   = description
  )
```

# Invited & Guest Lectures

```{r lectures}
lectures_data |>
  brief_entries(
    what  = title,
    when  = date,
    with  = context
  )
```

# Refereed Journal Articles

*Citations: `r .cites` | h-index: `r .hindex` | i10-index: `r .i10` — as of `r .metrics_date`*
*(via Google Scholar)*

## Published

```{r publications}
bibliography_entries("publications.bib") |>
  arrange(desc(issued)) |>
  mutate(
    author = map(author, \(x) {
      if (!is.null(x$family)) {
        x$family <- replace(x$family, x$family == "Miramonti", "\\textbf{Miramonti}")
      }
      x
    })
  )
```

`r if (params$show_manuscripts) "## Manuscripts in Progress"`

```{r manuscripts, eval=params$show_manuscripts}
manuscripts_data |>
  brief_entries(
    what = title,
    when = status,
    with = authors
  )
```

`r if (params$show_preprints) "## Preprints"`

```{r preprints, eval=params$show_preprints}
# ⚠️ Confirm authorship and section placement before v1.0.0
preprints_data |>
  brief_entries(
    what = glue("{title}. {repository}. doi:{doi}"),
    when = date,
    with = authors
  )
```

`r if (params$show_presentations) "# Papers Presented at Professional Meetings"`

```{r presentations, eval=params$show_presentations}
bibliography_entries("presentations.bib") |>
  arrange(desc(issued))
```

`r if (params$show_mentoring) "# Mentoring Experience"`

```{r mentoring, eval=params$show_mentoring}
mentoring_data |>
  brief_entries(
    what  = role,
    when  = dates,
    with  = glue("{program}, {institution}")
  )
```

`r if (params$show_training) "# Additional Professional Training"`

`r if (params$show_training) "## Nebraska Academy for Methodology, Analytics, & Psychometrics — Nebraska Methodology Applications"`

```{r training-mapapps, eval=params$show_training}
training_data |>
  filter(series == "Nebraska MAP Apps") |>
  brief_entries(
    what = title,
    when = date,
    with = presenter
  )
```

`r if (params$show_training) "## Nebraska Academy for Methodology, Analytics, & Psychometrics — Emerging Scholars Series"`

```{r training-emerging, eval=params$show_training}
training_data |>
  filter(series == "Emerging Scholars") |>
  brief_entries(
    what = title,
    when = date,
    with = presenter
  )
```

# Professional Service

```{r service}
service_data |>
  brief_entries(
    what  = role,
    when  = dates,
    with  = organization
  )
```

# Professional Associations

```{r associations}
associations_data |>
  brief_entries(
    what  = organization,
    when  = dates,
    with  = membership
  )
```

`r if (params$show_credentials) "# Professional Credentials"`

```{r credentials, eval=params$show_credentials}
credentials_data |>
  brief_entries(
    what  = credential,
    when  = status,
    with  = organization
  )
```

# Awards, Fellowships, & Scholarships

```{r awards}
awards_data |>
  brief_entries(
    what  = award,
    when  = dates,
    with  = organization
  )
```

# Technical Skills

`r if (params$show_lab_skills) "## Laboratory Assessments"`

```{r lab-skills, results="asis", eval=params$show_lab_skills}
cat(paste0("\\begin{itemize}\n",
           paste0("  \\item ", lab_skills, collapse = "\n"),
           "\n\\end{itemize}"))
```

## Software & Computing

```{r software}
software_data |>
  brief_entries(
    what = tools,
    with = category
  )
```

`r if (params$show_languages) "## Languages"`

```{r languages, eval=params$show_languages}
languages_data |>
  brief_entries(
    what  = language,
    with  = proficiency
  )
```

`r if (params$show_profiles) "# Online Profiles"`

```{r profiles, eval=params$show_profiles}
profiles_data |>
  brief_entries(
    what = platform,
    with = url
  )
```
