---
name: Amelia A.
surname: Miramonti
position: "Postdoctoral Researcher and Adjunct Faculty"
address: "Nebraska Evaluation and Research Center · University of Nebraska–Lincoln"
email: "amiramonti@nebraska.edu"
github: "amelia-m"
linkedin: "amelia-miramonti"
orcid: "0000-0002-0277-4064"
scholar: "AcbJlasAAAAJ"
researchgate: "Amelia-Miramonti"
www: "osf.io/zk8rv/"
headcolor: "009ACD"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::latexcv:
    theme: classic
engine: knitr
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(vitae)
library(tibble)
library(dplyr)
library(purrr)
library(glue)
library(conflicted)

conflicts_prefer(dplyr::filter, dplyr::select, .quiet = TRUE)

source("cv_data.R")
```

# Education

```{r education}
education_data |>
  detailed_entries(
    what  = degree,
    when  = dates,
    with  = institution,
    where = location,
    why   = details
  )
```

# Academic Professional Experience

```{r positions}
positions_data |>
  detailed_entries(
    what  = title,
    when  = dates,
    with  = unit,
    where = institution,
    why   = description
  )
```

# Invited & Guest Lectures

```{r lectures}
lectures_data |>
  brief_entries(
    what  = title,
    when  = date,
    with  = context
  )
```

# Refereed Journal Articles

*Citations: 1,559 | h-index: 17 | i10-index: 20 — as of 2025-04-28*
*(via Google Scholar)*

## Published

```{r publications}
bibliography_entries("publications.bib") |>
  arrange(desc(issued)) |>
  mutate(
    author = map(author, \(x) {
      if (!is.null(x$family)) {
        x$family <- replace(x$family, x$family == "Miramonti", "\\textbf{Miramonti}")
      }
      x
    })
  )
```

## Manuscripts in Progress

```{r manuscripts}
manuscripts_data |>
  brief_entries(
    what = title,
    when = status,
    with = authors
  )
```

## Preprints

```{r preprints}
# ⚠️ Confirm authorship and section placement before v1.0.0
preprints_data |>
  brief_entries(
    what = glue("{title}. {repository}. doi:{doi}"),
    when = date,
    with = authors
  )
```

# Papers Presented at Professional Meetings

```{r presentations}
bibliography_entries("presentations.bib") |>
  arrange(desc(issued))
```

# Mentoring Experience

```{r mentoring}
mentoring_data |>
  brief_entries(
    what  = role,
    when  = dates,
    with  = glue("{program}, {institution}")
  )
```

# Additional Professional Training

## Nebraska Academy for Methodology, Analytics, & Psychometrics — Nebraska Methodology Applications

```{r training-mapapps}
training_data |>
  filter(series == "Nebraska MAP Apps") |>
  brief_entries(
    what = title,
    when = date,
    with = presenter
  )
```

## Nebraska Academy for Methodology, Analytics, & Psychometrics — Emerging Scholars Series

```{r training-emerging}
training_data |>
  filter(series == "Emerging Scholars") |>
  brief_entries(
    what = title,
    when = date,
    with = presenter
  )
```

# Professional Service

```{r service}
service_data |>
  brief_entries(
    what  = role,
    when  = dates,
    with  = organization
  )
```

# Professional Associations

```{r associations}
associations_data |>
  brief_entries(
    what  = organization,
    when  = dates,
    with  = membership
  )
```

# Professional Credentials

```{r credentials}
credentials_data |>
  brief_entries(
    what  = credential,
    when  = status,
    with  = organization
  )
```

# Awards, Fellowships, & Scholarships

```{r awards}
awards_data |>
  brief_entries(
    what  = award,
    when  = dates,
    with  = organization
  )
```

# Technical Skills

## Laboratory Assessments

```{r lab-skills, results="asis"}
cat(paste0("\\begin{itemize}\n",
           paste0("  \\item ", lab_skills, collapse = "\n"),
           "\n\\end{itemize}"))
```

## Software & Computing

```{r software}
software_data |>
  brief_entries(
    what = tools,
    with = category
  )
```

## Languages

```{r languages}
languages_data |>
  brief_entries(
    what  = language,
    with  = proficiency
  )
```

# Online Profiles

```{r profiles}
profiles_data |>
  brief_entries(
    what = platform,
    with = url
  )
```
